Supporting Information

### 2016-08-19 portfolio/text/ms.Rmd
Edit captions and equations

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/fig1-jk.pdf}
\caption{
Trends in revenue and diversification over time.
(A) Map of fishing regions in Alaska, USA.
(B) Total revenue in billions of 20XX U.S. dollars from `r range_yrs[1]` to
`r range_yrs[2]` for multiple (grey) and single (blue) permit holders.
(C) Proportion of single permit holders for all fisheries (thick black line)
and with permit holders omitted each year who fished any of the
`r n_jacknifed` top species groups (thin lines).
(D) Mean effective diversity of species fished (Simpson's diversity index) 
for all fisheries (thick black line)
and with permit holders omitted each year who fished any of the
`r n_jacknifed` top species groups (thin lines).
}
\label{fig:ts}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/stan-across-strategy-variability.pdf}
\caption{Individuals who choose
permits with higher species diversity
have lower expected revenue variability.
On the y-axis, dots, thick lines, and thin lines represent posterior medians,
50\%, and 95\% credible intervals for
the `r nstr` most common permit strategies.
Thick black line, and dark and light grey shaded regions
indicate median, 50\%, and 95\% credible intervals
of strastegy-level regression built into the heirarchical model.
}
\label{fig:across}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/fig1-jk.pdf}
\caption{
Trends in revenue and diversification over time.
(A) Map of fishing regions in Alaska, USA.
(B) Total revenue in billions of 2009 U.S. dollars from `r range_yrs[1]` to
`r range_yrs[2]` for multiple (grey) and single (blue) permit holders.
(C) Proportion of single permit holders for all fisheries (thick black line)
and with permit holders omitted each year who fished any of the
`r n_jacknifed` top species groups (thin lines).
(D) Mean effective diversity of species fished (Simpson's diversity index) 
for all fisheries (thick black line)
and with permit holders omitted each year who fished any of the
`r n_jacknifed` top species groups (thin lines).
}
\label{fig:ts}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/stan-across-strategy-variability.pdf}
\caption{Individuals who fish
permits and permit combinations (permit strategies) with higher species diversity
have lower expected revenue variability.
On the y-axis, dots, thick lines, and thin lines represent posterior medians,
50\%, and 95\% credible intervals for
the `r nstr` most common permit strategies.
Thick black line, and dark and light grey shaded regions
indicate median, 50\%, and 95\% credible intervals
of strategy-level regression built into the hierarchical model.
Estimated variability represents expected standard deviation
at an average of about
`r mean_permit_days` combined fishing days across permits,
and for a permit holder who does not change
species diversity or days fished from year to year.
}
\label{fig:across}
\end{center}
\end{figure}

### 2016-08-19 portfolio/text/supp.Rnw
Edit captions and equations

\begin{align}
\gamma_{0,j}  &\sim \mathrm{N} \left(\gamma_0, \sigma^2_{\gamma_0}\right),\\
\gamma_{1,j}  &\sim \mathrm{N} \left(\gamma_1, \sigma^2_{\gamma_1}\right),\\
\gamma_{2,j}  &\sim \mathrm{N} \left(\gamma_2, \sigma^2_{\gamma_2}\right).
\end{align}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=5in]{../figs/stan-main-effects.pdf}
\caption{Main effects from the hierarchical model 
predicting revenue (b or $\beta$) and variability (g or $\gamma$) in revenue.
The coefficient $u_1$ represents a strategy level predictor
relating mean species diversity of a strategy
to the expected magnitude of residual error.}
\label{fig:fe}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.06\textwidth]{../figs/stan-str-posteriors-dot.pdf}
\caption{Estimates of within strategy effects from the hierarchical model. 
Panels refer in order to $\gamma_0$ (g0), $\gamma_1$ (g1), $\gamma_2$ (g2),
$\beta_1$ (b1), and $\beta_2$ (b2) from Eqns \ref{eq:mean} and \ref{eq:cv}.
Shown are medians (dots) and 50\% and 90\% credible intervals
(thick and thin line segments).
Strategies are ordered from high to low mean
species diversity from top to bottom.}
\label{fig:re}
\end{center}
\end{figure}

>>>>

\begin{align}
\gamma_{0,j}  &\sim \mathrm{N} \left(\gamma_0 + \eta_1 M_j + \eta_2 A_j, \sigma^2_{\gamma_0}\right),\\
\gamma_{1,j}  &\sim \mathrm{N} \left(\gamma_1, \sigma^2_{\gamma_1}\right),\\
\gamma_{2,j}  &\sim \mathrm{N} \left(\gamma_2, \sigma^2_{\gamma_2}\right).
\end{align}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=5in]{../figs/stan-main-effects.pdf}
\caption{Main effects from the hierarchical model
predicting revenue ($\beta$) and variability ($\gamma$) in revenue.
The $\eta$ coefficients represents strategy-level predictors
relating mean species diversity and mean days fished
within a strategy
(both centered by their means and divided by
two times their standard deivations)
to the magnitude of residual error.}
\label{fig:fe}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.06\textwidth]{../figs/stan-str-posteriors-dot.pdf}
\caption{Estimates of within-strategy effects from the hierarchical model.
Panels refer to parameters in Eqns \ref{eq:mean} and \ref{eq:cv}.
Shown are medians (dots) and 50\% and 95\% credible intervals
(thick and thin line segments).
Strategies are ordered from high to low mean
species diversity from top to bottom.}
\label{fig:re}
\end{center}
\end{figure}
